A Flexible Generator of Constrained Global Optimization Test Problems

### 2018-07-30 2018/LeGo/LeGo.tex
final

\begin{abstract}
In the present work, further development of an approach to constructing test global 
optimization problems with nonlinear constraints is considered. In the generated problems, the 
location of the global minimum is known. The considered generator is featured by an option of 
specifying desired number of constraints and the fraction of feasible domain relative to the 
whole global search domain. In the updated version of the generator, the options of forming the 
problems with a conditional minimum located at the boundary of the feasible domain and of 
specifying the number of constraints active at the minimizer have been added. The 
demonstration of the developed approach is given on the example of a known index method for 
solving complex multiextremal optimization problems with non-convex constraints.
\end{abstract}

@@

In the present paper, the methods for generating the global optimization test problems with non-convex constraints
\begin{eqnarray}
&\varphi(y^\ast)=\min{\left\{\varphi(y):y\in D, \; g_i(y)\leq 0, \; 1 \leq i \leq m\right\}}, 
\label{i_problem} \\
&D=\left\{y\in R^N: a_i\leq y_i \leq b_i, 1\leq i \leq N\right\} \label{D}
\end{eqnarray}
are considered. The objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and 
the left-hand sides $g_i(y), \; 1\leq i \leq m,$ of the constraints are supposed to satisfy the 
Lipschitz condition
\[ \left|g_i(y')-g_i (y'')\right| \leq L_i \left\|y'-y'' \right\|, \; y',y''\in D, \; 1\leq i \leq m+1. \]
with the Lipschitz constants unknown a priori. The analytical formulae of the problem functions 
may be unknown, i.e. these ones may be defined by an algorithm for computing the function 
values in the search domain (so called ``black-box''-functions).

@@

The problem of developing the generators of the multiextremal test problems with non-convex 
constraints is a relevant one since standard approach to investigating and comparing the 
global optimization algorithms is based on solving a series of test problems.
Well known generators generate the problems without constraints as a rule. For example, a 
method for constructing two-dimensional test functions has been proposed by Grishagin (its 
description can be found in \cite{Grishagin1997,Grishagin2015}). Another generator 
(\textit{GKLS generator}) for the functions of arbitrary dimensionality has been proposed in 
\cite{Gaviano2003}.  GKLS generator has been successfully applied in the investigation of some global 
optimization methods \cite{Paulavicius2014,Sergeyev2015,Grishagin2018}.
Based on the GKLS generator, an approach to constructing the constrained problems has been 
proposed (Emmental-type GKLS-based test problems \cite{Sergeyev2017}). In this generator, 
the modified GKLS-function was used as the objective function, the constraints were the 
exterior of the balls with given centers and radii. The use of other objective functions and/or 
constraints was not allowed that was a disadvantage of this generator.

@@

\begin{itemize}
\item The possibility to generate the problems with the constrained minimizer located at the 
boundary of the feasible domain.
\item The possibility to control the number of constraints active in the optimum point.
\end{itemize}

@@

The generator GCGen (Global Constrained optimization problem Generator) which allows to 
generate the test global optimization problems with $m$ constraints has been proposed in \cite{Gergel2017}. In this paper, the rules, which allow formulating the constrained global optimization problems have been proposed so that:
\begin{itemize}
	\item one could control the size of feasible domain with respect to the whole domain of 
the parameters' variation;
	\item the global minimizer of the objective function would be known a priori taking into 
account the constraints;
	\item the global minimizer of the objective function without accounting for the 
constraints would be out of the feasible domain.
\end{itemize}

The location of the minimizer at the boundary of the feasible domain is an important 
property featuring the applied constrained optimization problems. 
When generating the problems according to the scheme described in \cite{Gergel2017}, 
the constrained minimum point, in general, will be located inside the feasible domain. Therefore, the 
options of shifting the minimizer to the boundary of the feasible domain as well of 
controlling the number of the active constraints in this one have been added in the new version 
of the problem generator.

@@

In the case, when it is necessary to generate a problem with a number of active 
constraints in the minimizer not less than $S$, the rules are modified as follows.
\begin{enumerate}
\item A problem with an arbitrary location of a constrained minimizer $\overline{y}$ is 
generated;
\item From the point $\overline{y}$, a coordinate search of a feasible point $y^*$, for which at 
least one constraint is active i. e. there is such index $j, 1 \leq j\leq m$ that $\left|g_j(y^*)\right| 
\leq \delta$ is performed with a predefined step $h$.
\item A rough estimate $y^*$ obtained is refined by a local method. 
\item The number $K$ of the constraints active at the point $y^*$ is determined.
\item If $K<S$, $S-K$ constraints are selected from the set of the inactive ones, and and these 
ones are set to be the active by adding a positive parameter $q$ to the right hand side.
\item The coordinate transformation transferring the point $\overline{y}$ to the point $y^*$ is 
performed. This way, the objective function reaches its minimum at the boundary of the feasible 
domain with the number of active constraints not less than $S$. 
\end{enumerate}

>>>>

\begin{abstract}
In the present work, further development of an approach to constructing test global 
optimization problems with nonlinear constraints is considered. In the generated problems, the 
location of the global minimum is known. The considered generator is featured by an option of 
specifying desired number of constraints and the fraction of feasible domain relative to the 
whole global search domain. In the updated version of the generator, the options of forming the 
problems with a conditional minimum located at the boundary of the feasible domain and of 
controlling the number of constraints active at the minimizer have been added. The 
demonstration of the developed approach is given on the example of a known index method for 
solving complex multiextremal optimization problems with non-convex constraints.
\end{abstract}

@@

In the present paper, the methods for generating global optimization test problems with non-convex constraints
\begin{eqnarray}
&\varphi(y^\ast)=\min{\left\{\varphi(y):y\in D, \; g_i(y)\leq 0, \; 1 \leq i \leq m\right\}}, 
\label{i_problem} \\
&D=\left\{y\in R^N: a_i\leq y_i \leq b_i, 1\leq i \leq N\right\} \label{D}
\end{eqnarray}
are considered. The objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and 
the left-hand sides $g_i(y), \; 1\leq i \leq m,$ of the constraints are supposed to satisfy the 
Lipschitz condition
\[ \left|g_i(y')-g_i (y'')\right| \leq L_i \left\|y'-y'' \right\|, \; y',y''\in D, \; 1\leq i \leq m+1, \]
with the Lipschitz constants unknown a priori. The analytical formulae of the problem functions 
may be unknown, i.e. they may be defined by an algorithm for computing the function 
values in the search domain (so called ``black-box''-functions).

@@

The problem of developing the generators of the multiextremal test problems with non-convex 
constraints is relevant since classes of test problems are used usually for investigating and comparing global optimization algorithms.
Well known generators construct the problems without constraints as a rule. For example, a 
method for constructing two-dimensional test functions has been proposed by Grishagin (its 
description can be found in \cite{Grishagin1997,Grishagin2015}). Another generator 
(\textit{GKLS generator}) for the functions of arbitrary dimensionality has been proposed in 
\cite{Gaviano2003}.  GKLS generator has been successfully applied in the investigation of several global 
optimization methods \cite{Paulavicius2014,Sergeyev2015,Grishagin2018}.
Based on the GKLS generator, an approach to constructing the constrained problems has been 
proposed (Emmental-type GKLS-based test problems \cite{Sergeyev2017}). In this generator, 
the modified GKLS-function was used as the objective function, the constraints were the 
exterior of the balls with given centers and radii. The use of other objective functions and/or 
constraints was not allowed that was a disadvantage of this generator.

@@

\begin{itemize}
\item The possibility to generate the problems with the constrained minimizer located at the 
boundary of the feasible domain.
\item The possibility to control the number of constraints active at the optimum point.
\end{itemize}

@@

The generator GCGen (Global Constrained optimization problem Generator) which allows to 
generate the test global optimization problems with $m$ constraints has been proposed in \cite{Gergel2017}. In the mentioned paper the rules which allow formulating the constrained global optimization problems have been proposed so that:
\begin{itemize}
	\item one could control the size of feasible domain with respect to the whole domain of 
the parameters' variation;
	\item the global minimizer of the objective function would be known a priori taking into 
account the constraints;
	\item the global minimizer of the objective function without accounting for the 
constraints would be out of the feasible domain;
	\item the value of the gradient at the global solution of the constrained problems is zero.
\end{itemize}

The location of the minimizer at the boundary of the feasible domain is an important 
property featuring the applied constrained optimization problems. 
When generating the problems according to the scheme described in \cite{Gergel2017}, 
the constrained minimum point, in general, will be located inside the feasible domain. Therefore, the 
options of shifting the minimizer to the boundary of the feasible domain as well of 
controlling the number of the active constraints at the global solution have been added in the new version 
of the problem generator.

@@

In the case, when it is necessary to generate a problem with a number of active 
constraints at the minimizer not less than $S$, the rules are modified as follows.
\begin{enumerate}
\item A problem with an arbitrary location of a constrained minimizer $\overline{y}$ is 
generated;
\item From the point $\overline{y}$, a coordinate search of a feasible point $y^*$, for which at 
least one constraint is active (i.e. there is such index $j, 1 \leq j\leq m$, that $\left|g_j(y^*)\right| 
\leq \delta$) is performed with a predefined step $h$.
\item A rough estimate $y^*$ obtained is refined by a local method. 
\item The number $K$ of the constraints active at the point $y^*$ is determined.
\item If $K<S$, $S-K$ constraints are selected from the set of the inactive ones, and these 
ones are set to be the active by adding a positive parameter $q$ to the right hand side.
\item The coordinate transformation transferring the point $\overline{y}$ to the point $y^*$ is 
performed. This way, the objective function reaches its minimum at the boundary of the feasible 
domain with the number of active constraints not less than $S$. 
\end{enumerate}
